Commutative character sheaves and geometric types for supercuspidal representations

### 2020-07-24 Geometric types.tex

Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we return to the task of geometrizing Yu type data. 
The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
In order to use these tools we must restrict our attention to Yu type data that satisfy a technical condition, appearing in Section~\ref{ssec:geotypes} as Hypothesis~\ref{H1}. 
Granting this hypothesis, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
With this theorem, we provide all of the ingredients needed to geometrize a class of supercuspidal representations of arbitrary depth.

>>>>

Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we return to the task of geometrizing Yu type data. 
The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.

In order to use these tools we must restrict our attention to Yu type data that satisfy a technical condition, appearing in Section~\ref{ssec:geotypes} as Hypothesis~\ref{H1}. 
Granting this hypothesis, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
With this theorem, we provide all of the ingredients needed to geometrize a class of supercuspidal representations of arbitrary depth.

Yu's construction has been revisited recently by several authors.
Hakim \cite{hakim:18a}*{\S 2.1} gives an alternate construction beginning with a
representation of a compact-mod-center subgroup of $G$.
Unfortunately, this ingredient does not lend itself to geometrization using our techniques.
In contrast, Kaletha \cite{kaletha:19a} has given a construction in terms of a
tame elliptic maximal torus $S \subset G$ and a character $\theta$ of $S$.
The pair $(S, \theta)$ can already be geometrized using \cite{cunningham-roe:13a} since $S$ is commutative.
However, Kaletha's construction only produces a subset of Yu's supercuspidal representations \cite{kaletha:19a}*{Prop. 3.7.14}, so we phrase our geometrization in terms of Yu's original construction.
